---
title: "Reproducible Research: Peer Assessment 1"
author: Max Lyons
date: 6/26/2016
---
Load ggplot2 for plotting, and dplyr for data wrangling
```{r}
library(ggplot2)
library(dplyr)
```

## Loading and preprocessing the data
First we will unzip the wearable technology data and load it into R
```{r}
unzip("activity.zip")
activity <- read.csv("activity.csv",header=T,stringsAsFactors = FALSE)
head(activity)
```

## What is mean total number of steps taken per day?
To find the mean number of steps taken each day, we first need to create a 
dataframe of steps by day
```{r}
day_activity <- activity %>% group_by(date) %>% 
    summarise(steps = sum(steps, na.rm = TRUE))
```
We can then make a histogram of total steps taken each day
```{r}
steps_hist <- ggplot(day_activity, aes(x = steps)) + 
    geom_histogram(binwidth = 1000)
steps_hist <- steps_hist + scale_y_continuous("number of days",breaks=0:10)
steps_hist <- steps_hist + 
    labs(title = "Distribution of Total Steps Taken Each Day", x="total steps")
steps_hist
```
And use the same dataframe to calculate the mean and median of total steps
```{r}
totalsteps_mean <- mean(day_activity$steps)
totalsteps_median <- median(day_activity$steps)
```
Mean = `r totalsteps_mean`  
Median = `r totalsteps_median`


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
